Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-01-06 paper/tidy-missing-data-paper.Rmd
relabel from 3 features to 4

Three features are added to the shadow matrix to facilitate analysis:

@@

2. Special missing values: Values in the shadow matrix can be "special" missing values, indicated as `NA_suffix`, where "suffix" is a very short message of the type of missings.

3. Cohesiveness: Binding the shadow matrix column-wise to the original data creates a cohesive _nabular_ data form, useful for visualization and summaries.

@@

>>>>

Four features are added to the shadow matrix to facilitate analysis:

@@

1. Missing value label: A simple label to the shadow matrix clear, "NA" and "!NA" for missing and not missing, represented as 0 and 1 (see Figure \@ref(fig:shadow-matrix-progress) parts 2 and 3 below).

1. Special missing values: Building on 2, the values in the shadow matrix can be "special" missing values, indicated as `NA_suffix`, where "suffix" is a very short label of the type of missings, and the underlying values are >= 2.

1. Cohesiveness: Binding the shadow matrix column-wise to the original data creates a cohesive _nabular_ data form, useful for visualization and summaries.

@@

(**consider removing these longer expansions of these points?**)
